Benchmarking on Rigetti architecture

### 2022-07-05 txt/manuscript.tex
reformulate structure of text

@@

Let $M_{d_1,d_2}$ be the set of all matrices of dimension $d_1 \times d_2$ over
the field $\mathbb{C}$. For  simplicity notation, square matrices will be 
denoted by
$M_d$.  The subset of $M_d$ consisting of Hermitian matrices of dimension $d$ 
will  be  denoted  by $\HH_d$,  while  the  set  of  positive semidefinite 
matrices of dimension $d$ by $\HH_d^+$. The set of quantum states, that is 
positive semidefinite operators having
trace equal to one, will be denoted $\Omega_d$.  The subset of $M_d$ consisting of 
unitary matrices will be denoted by
$\UU_d$, while its subgroup of diagonal unitary operators will be denoted by
$\DD \UU_d$.  We will also need a linear
mapping transforming $M_{d_1}$ into $M_{d_2}$, which will be denoted \begin{equation}
\Phi: M_{d_1 } \rightarrow M_{d_2}.
\end{equation} Finally, we introduce a special subset of all mappings $\Phi$, called quantum channels, which are completely positive
and trace preserving (CPTP).
Mostly, we will use the unitary channels
$\Phi_{U}$ which are defined as $\Phi_U(\cdot) = U \cdot U^\dagger$ for  $U \in 
\UU_d$. A general quantum
measurement, that is a positive operator valued measure (POVM) $\PP$ is a
collection of positive semidefinite operators $\{E_1, \ldots, E_m \}$ called
\emph{effects}, which sum up to identity, \ie $ \, \, \sum_{i=1}^m E_i = \1$. If
all the effects are rank-one projection operators, then such a measurement is
called von Neumann measurement. Every von Neumann measurement can be
parameterized by a unitary matrix and hence we will use the notation $\PP_{U}$
for a von Neumann measurement with effects $\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$,
where $\ket{u_i}$ is the $i+1$-th column of the unitary matrix $U$. The action of
quantum measurement $\PP_{U}$ on some state $\rho \in \Omega_d$ can be
expressed as the action of a quantum channel
$
\PP_{U} : \rho \rightarrow \sum_{i=0}^{d-1} \bra{u_i} \rho \ket{u_i} \proj{i}.
$ Every von Neumann measurement  $\PP_{U}$ can be also rewritten as $\Delta 
\circ \Phi_{(UE)^\dagger}$, where $\Delta$ denotes the completely dephasing 
channel.

@@

In case then 
we consider the discrimination setup between two von Neumann 
measurements $\PP_U$ and $\PP_\Id$, $U\in \UU_d$ we obtain that (from Theorem 1 \cite{puchala2018strategies})
\begin{equation}
\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} - 
\Phi_\Id\|_\diamond,
\end{equation}
where $\Phi_U$ is unitary channel and 
$\diaguni_d$ be the set of diagonal unitary matrices of dimension $d$

@@

\subsubsection{Rigetti architecture's limits/ practical solutions}
\todo[inline]{nie wiem, moze tu o conditional measurement i o sposobach 
ominiecia tego problemu - postselekcja i kontrolowana unitarka}

@@

\begin{figure}[h!]
\centering
\includegraphics[scale=1.2]{pics/theoretical_scheme}
\caption{Theoretical discrimination scheme}
\label{fig:theoretical_scheme}
\end{figure}

@@

>>>>

\subsubsection{Rigetti architecture's limits/ practical solutions}

\todo[inline]{PAMIETAJ O DAGGERACH !!!}

\begin{figure}[h!]
	\centering
	\includegraphics[scale=1.2]{pics/theoretical_scheme}
	\caption{Theoretical discrimination scheme}
	\label{fig:theoretical_scheme}
\end{figure}
\todo[inline]{konretne przyklady zobaczymy potem... }

@@

Let $M_{d_1,d_2}$ be the set of all matrices of dimension $d_1 \times d_2$ over
the field $\mathbb{C}$. For  simplicity notation, square matrices will be 
denoted by
$M_d$.  The subset of $M_d$ consisting of Hermitian matrices of dimension $d$ 
will  be  denoted  by $\HH_d$,  while  the  set  of  positive semidefinite 
matrices of dimension $d$ by $\HH_d^+$. The set of quantum states, that is 
positive semidefinite operators having
trace equal to one, will be denoted $\Omega_d$.  The subset of $M_d$ consisting of 
unitary matrices will be denoted by
$\UU_d$, while its subgroup of diagonal unitary operators will be denoted by
$\DD \UU_d$.  We will also need a linear
mapping transforming $M_{d_1}$ into $M_{d_2}$, which will be denoted \begin{equation}
\Phi: M_{d_1 } \rightarrow M_{d_2}.
\end{equation} 
\todo[inline]{nie mowimy channel} 
Finally, we introduce a special subset of all mappings $\Phi$, called quantum channels, which are completely positive
and trace preserving (CPTP).
Mostly, we will use the unitary channels
$\Phi_{U}$ which are defined as $\Phi_U(\cdot) = U \cdot U^\dagger$ for  $U \in 
\UU_d$. A general quantum
measurement, that is a positive operator valued measure (POVM) $\PP$ is a
collection of positive semidefinite operators $\{E_1, \ldots, E_m \}$ called
\emph{effects}, which sum up to identity, \ie $ \, \, \sum_{i=1}^m E_i = \1$. If
all the effects are rank-one projection operators, then such a measurement is
called von Neumann measurement. Every von Neumann measurement can be
parameterized by a unitary matrix and hence we will use the notation $\PP_{U}$
for a von Neumann measurement with effects $\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$,
where $\ket{u_i}$ is the $i+1$-th column of the unitary matrix $U$. The action of
quantum measurement $\PP_{U}$ on some state $\rho \in \Omega_d$ can be
expressed as the action of a quantum channel
$
\PP_{U} : \rho \rightarrow \sum_{i=0}^{d-1} \bra{u_i} \rho \ket{u_i} \proj{i}.
$ Every von Neumann measurement  $\PP_{U}$ can be also rewritten as $\Delta 
\circ \Phi_{(UE)^\dagger}$, where $\Delta$ denotes the completely dephasing 
channel.

@@

In case then 
we consider the discrimination setup between two von Neumann 
measurements $\PP_U$ and $\PP_\Id$, $U\in \UU_d$ we obtain that (from Theorem 1 \cite{puchala2018strategies})
\begin{equation}
\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} - 
\Phi_\Id\|_\diamond,
\end{equation}
where $\Phi_U$ is unitary channel and 
$\diaguni_d$ be the set of diagonal unitary matrices of dimension $d$.

@@

@@

@@

\todo[inline]{obwody }
\todo[inline]{TU WYNIKI Z RIGETTIEGO}
